---
title: "HW5 notebook"
output: html_notebook
---
 
Here is the first method for overlaying shape data on a raster.

Use the following packages (install them first), then use them via
the library() call: tmap, tmaptools, rgdal, sp, OpenStreetMap, osmdata

These calls are useful: readOGR(), tmaptools::read_osm(),
tm_shape(), tm_raster(), tm_dots()

1. readOGR() your shapefile, store it in a var
2. read_osm() the bbox of #1 above, store it in a var
3. do tm_shape() on #2 + tm_raster() +
tm_shape() on #1 + tm_dots() to specify point color and size

```{r}
library(rgdal)
ogr <- readOGR(dsn = "mygeodata/placemarks.shp")
osm <- read_osm(ogr)
tm_shape(osm) + tm_raster() + tm_shape(ogr) + tm_dots(size = 1, col='red')
```

And here's the second.

Use these packages: PBSmapping, ggmap
And these calls: importShapefile(), as.data.frame(), get_map(), ggmap(), 
geom_point()

1. importShapefile() into a var
2. convert it (#1 above) to a dataframe, store it in a var
3. get_map() with a location that's in your collection of (lat,long),
store it in a var
4. do ggmap() on #3, + geom_point() on #2

```{r}
library(ggmap)
file<-importShapefile("mygeodata/placemarks")
df <- data.frame(file)
map<-get_map(location = c(df['X'][1,],df['Y'][1,]),zoom = 15)
ggmap(map) + geom_point(data=df, aes(x=X, y=Y), color='red')
```


